Dynamics of Laterally Propagating Flames in X-ray Bursts. I. Burning Front Structure

### 2020-03-03 xrb/submit/paper.tex
Incorporate Yuri's comments

\added{The computational expense of the problem necessitated several approximations
to make the simulations of \citet{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal}
and \citet{Cavecchi2019} tractable. The first was the assumption of vertical hydrostatic equilibrium,
which allowed them to filter out vertically propagating sound waves that would otherwise
have limited the timestep. This enabled them to reach the simulation times (on the
order of seconds) needed to capture the rise of the burst, but they could not model
vortical fluid motions driven by effects such as turbulence and convection. These can
facilitate mixing and help to accelerate the propagation of the flame front. They also
included only the triple-$\alpha$ process in their implementation of nuclear burning,
and use a fixed, constant opacity across the entire domain for each simulation run (although
they explore the dependence of the flame propagation speed on this opacity value).
Our simulations relax the assumption of vertical hydrostatic equilibrium, and implement
a more complete set of nuclear reactions and opacities. However, as discussed later, this
comes at the expense of a different set of approximations.}

@@

\added{
\citet{cavecchi:2013} ran simulations at rotation rates of $450$ Hz exploring a range of opacities.
Accounting for the boosting, we would expect to see our 10/10 flame propagate at $\sim 2.25$ times
the speed of these $450$ Hz runs, but instead the speeds range from $4.5$ to $7$ times those reported in
\citet{cavecchi:2013}. The additional boost may come from cyclic fluid motions that would have been
disallowed in the $450$ Hz runs by the enforcement of vertical hydrostatic equilibrium (we already saw
that hydrodynamic effects can accelerate the burning front in our comparison with the 1D flames). The
inclusion of reaction chains beyond triple-$\alpha$ may also increase energy generation and consequently the
propagation speed.}

>>>>

\added{The computational expense of the problem necessitated several approximations
to make the simulations of \citet{cavecchi:2013, art-2015-cavecchi-etal, art-2016-cavecchi-etal}
and \citet{Cavecchi2019} tractable. The first of these approximations was the assumption of
vertical hydrostatic equilibrium, which allowed them to use a less refined grid and filter out
vertically propagating sound waves that would otherwise have limited the timestep. This
enabled them to reach the simulation times (on the order of seconds) needed to capture the rise
of the burst, but they could not fully resolve vortical fluid motions driven by effects such as
turbulence and convection. These can facilitate mixing and help to accelerate the propagation of
the flame front. They also included only the triple-$\alpha$ process in their implementation of
nuclear burning, and used a fixed, constant opacity across the entire domain for each simulation
run (although they explored the dependence of the flame propagation speed on this opacity value).
Our simulations relax the assumption of vertical hydrostatic equilibrium, and implement
a more complete set of nuclear reactions and opacities. However, as discussed later, this
comes at the expense of a different set of approximations.}

@@

\added{
\citet{cavecchi:2013} ran simulations at rotation rates of $450$ Hz exploring a range of opacities.
Accounting for the boosting, we would expect to see our 10/10 flame propagate at $\sim 2.25$ times
the speed of these $450$ Hz runs, but instead the speeds range from $4.5$ to $7$ times those reported in
\citet{cavecchi:2013}. The additional boost may come from cyclic fluid motions that would have been
underresolved in the $450$ Hz runs due to the enforcement of vertical hydrostatic equilibrium (we already saw
that hydrodynamic effects can accelerate the burning front in our comparison with the 1D flames). The
inclusion of reaction chains beyond triple-$\alpha$ may also increase energy generation and consequently the
propagation speed.}
